---
title: "county-data-summary"
output: html_document
---

```{r, include=FALSE}

# Population Summary Data for use in markdown text
first.year.pop.county <- ofm.pop %>% filter(Jurisdiction == paste0(current.county, " County") & Year == first.year) %>% select(Estimate) %>% as.numeric
last.year.pop.county <- ofm.pop %>% filter(Jurisdiction == paste0(current.county, " County") & Year == last.year) %>% select(Estimate) %>% as.numeric

# Create Line Chart for Total County Population
working.data <- ofm.pop %>%
  filter(Jurisdiction == paste0(current.county, " County"))

total.county <- create_line_chart(w.data = working.data, w.x = "Year", w.y = "Estimate", w.color = "Jurisdiction", w.ltype = "twodash", w.lwidth = 1.5, w.palette = psrc_colors)

# Create Stacked Bar Chart for County Population by Incorporated/Unincorporated Population
working.data <- ofm.pop %>%
  filter(Jurisdiction %in% c(paste0("Incorporated ",current.county, " County"), paste0("Unincorporated ",current.county, " County")))

incorporation.county <- create_bar_chart(w.data = working.data, w.x = "Year", w.y = "Estimate", w.color = "Jurisdiction", w.bartype = "stack", w.transparent = 1.0, w.palette = psrc_colors, x.type = "continuous")

# Create Bar Chart for City Population by County
working.data <- ofm.pop %>%
  filter(Filter ==4 & County == current.county & Year == last.year) %>%
  arrange(desc(Estimate))

county.cities <- create_facet_bar_chart(working.data, "Jurisdiction", "Estimate" , "Jurisdiction", "PopRange", "free")

```

## `r paste0(current.county," County")`

`r toString(paste0(current.county, " County"))` was home to **`r toString(format(round(as.numeric(first.year.pop.county), -2), nsmall=0, big.mark=","))`** people in `r toString(format(as.character(first.year)))`. By `r toString(format(as.character(last.year)))`, the total population of the county had grown to more than **`r toString(format(round(as.numeric(last.year.pop.county), -2), nsmall=0, big.mark=","))`** people, an increase of **`r toString(format(round(as.numeric(last.year.pop.county - first.year.pop.county), -1), nsmall=0, big.mark=","))`** people over `r toString(format(round(as.numeric(last.year - first.year), 0), nsmall=0, big.mark=","))` years.

### `r paste0(current.county," County")` Total Population
This is the total population of the county.
```{r, echo=FALSE}

total.county

```

### `r paste0(current.county," County")` Incorporated Area Population
This is a stacked bar by incorporation status

```{r, echo=FALSE}

incorporation.county

```

### Population of Cities and Towns in `r paste0(current.county," County")`: `r toString(format(as.character(last.year)))`
This is a plot of population for every city in the county


```{r, echo=FALSE}

county.cities

```