---
title: "county-data-summary"
output: html_document
---

```{r, include=FALSE}

# Population Summary Data for use in markdown text
first.year.pop.county <- ofm.pop %>% filter(Jurisdiction == paste0(current.county, " County") & Year == first.year) %>% select(Estimate) %>% as.numeric
last.year.pop.county <- ofm.pop %>% filter(Jurisdiction == paste0(current.county, " County") & Year == last.year) %>% select(Estimate) %>% as.numeric

# Create Line Chart for Total County Population
current.filter <- 1

working.data <- ofm.pop %>%
  filter(Filter == current.filter & County == current.county)

total.county <- create_line_chart(w.data = working.data, w.x = "Year", w.y = "Estimate", w.color = "Jurisdiction", w.ltype = "twodash", w.lwidth = 1.5, w.palette = psrc_colors)

# Create Stacked Bar Chart for County Population by Incorporated/Unincorporated Population
current.filter <- c(2,3)

working.data <- ofm.pop %>%
  filter(Filter %in% current.filter & County == current.county)

incorporation.county <- create_bar_chart(w.data = working.data, w.x = "Year", w.y = "Estimate", w.color = "Jurisdiction", w.bartype = "stack", w.transparent = 1.0, w.palette = psrc_colors)

# Create Bar Chart for City Population by County
current.filter <- c(4)

working.data <- ofm.pop %>%
  filter(Filter %in% current.filter & County == current.county & Year == last.year) %>%
  arrange(desc(Estimate))

city.county <- ggplot()
city.county <-  ggplotly(city.county +
  geom_col(data = working.data, 
           aes(x = reorder(Jurisdiction, -Estimate), y = Estimate, fill = Jurisdiction),
           color = "black",
           alpha = 1.0,
           position = "dodge") +
    labs(x = NULL, y = NULL) +
    #scale_fill_manual(values= psrc_colors) +
    scale_y_continuous(labels = label_comma() ) +
    theme(plot.title = element_text(size = 10, face = 'bold'),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.line = element_blank(),
          panel.background = element_blank(),
          panel.grid.major.y = element_line(colour="#BBBDC0",size = 0.25),
          panel.grid.minor.y = element_line(colour="#BBBDC0",size = 0.25),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          text = element_text(family = "Segoe UI"),
          legend.position = "none",
          legend.title = element_blank())+
    facet_wrap(vars(PopRange), scales = "free") +
    theme(legend.position = "none"))

```

## `r paste0(current.county," County")`

`r toString(paste0(current.county, " County"))` was home to **`r toString(format(round(as.numeric(first.year.pop.county), -2), nsmall=0, big.mark=","))`** people in `r toString(format(as.character(first.year)))`. By `r toString(format(as.character(last.year)))`, the total population of the county had grown to more than **`r toString(format(round(as.numeric(last.year.pop.county), -2), nsmall=0, big.mark=","))`** people, an increase of **`r toString(format(round(as.numeric(last.year.pop.county - first.year.pop.county), -1), nsmall=0, big.mark=","))`** people over `r toString(format(round(as.numeric(last.year - first.year), 0), nsmall=0, big.mark=","))` years.

### `r paste0(current.county," County")` Total Population
This is the total population of the county.
```{r, echo=FALSE}

total.county

```

### `r paste0(current.county," County")` Incorporated Area Population
This is a stacked bar by incorporation status

```{r, echo=FALSE}

incorporation.county

```

### Population of Cities and Towns in `r paste0(current.county," County")`: `r toString(format(as.character(last.year)))`
This is a plot of population for every city in the county


```{r, echo=FALSE}

city.county

```