---
title: "county-data-summary"
output: html_document
---

```{r, include=FALSE}

```

## `r paste0(current.county," County")`

`r toString(paste0(current.county, " County"))` was home to **`r toString(format(round(as.numeric(first.year.pop.county), -2), nsmall=0, big.mark=","))`** people in `r toString(format(as.character(first.year)))`. By `r toString(format(as.character(last.year)))`, the total population of the county had grown to more than **`r toString(format(round(as.numeric(last.year.pop.county), -2), nsmall=0, big.mark=","))`** people, an increase of **`r toString(format(round(as.numeric(last.year.pop.county - first.year.pop.county), -1), nsmall=0, big.mark=","))`** people over `r toString(format(round(as.numeric(last.year - first.year), 0), nsmall=0, big.mark=","))` years.

### `r paste0(current.county," County")` Total Population
This is the total population of the county.
```{r, echo=FALSE}

total.county

```

### `r paste0(current.county," County")` Incorporated Area Population
This is a stacked bar by incorporation status

```{r, echo=FALSE}

incorporation.county

```

### Population of Cities and Towns in `r paste0(current.county," County")`: `r toString(format(as.character(last.year)))`
This is a plot of population for every city in the county


```{r, echo=FALSE}

county.cities

```