---
title: "Happy Accidents"
output: 
  html_document:
    theme: readable
    toc: true
    toc_depth: 5
    toc_float: true
    
---

Welcome to my Happy Little World. Let's build something together.

```{r setup, echo=TRUE}

library(knitr)
happy_accidents <- file.path(getwd() ,'bob-ross.jfif')
include_graphics(happy_accidents)

```

Syntax in your Markdown document is used to "encode" or build your page. Let's start with **headings**. Wait - notice that **bold**, why did that happen? Because the characters before and after the word tell the encoder that you want the text to be **bold**!

What about Headings - they are defined by the "#" sign

# Heading 1 
For a PSRC data example, think *Regional Summary*

## Heading 2
Next level down, how about *County Summary*

### Heading #3
Next level, how about *Regional Geographies by County*

Wait - why are things randomly *italicized*? You guessed it, it is that magic "*" 

Even though size and color changes with headings, never use headers for their looks - they define things including chapters in a table of contents. If you want a good list of markdown syntax in R, use the cheatsheet that is accessible with *Help - Cheatsheets - R Markdown Cheatsheet*.


```{r fig.cap = "<b><i>image from Pinterest</b></i>", fig.align='center',include=FALSE}
include_graphics(happy_accidents)
```

Where the heck is my picture? It is left out because **include** is FALSE. Let's try the same thing using **echo=FALSE**

```{r fig.cap = "<b><i>image from Pinterest</b></i>", fig.align='center',echo=FALSE}
include_graphics(happy_accidents)
```

There is Bob again, things are right in the world!

Let's look at one last useful feature in text before we move along. What if you want the text to be responsive to a change in a variable? Let's try this.

```{r echo=TRUE}

last.year <- "I hate 2020!"
this.year <- "Things are slowly getting better in 2021!"

```

To show the text **inline** is done with:
`r last.year` but **`r this.year`**

Bet you ended up with the text on one line - to add a break in markdown, put **2** spaces at the end of a sentence:

To show the text **inline** is done with:  
`r last.year` but **`r this.year`**

Enough with this world - let's get to the OFM data!